Component response rate variation underlies the stability of highly complex finite systems

### 2020-03-26 notebook/SI.Rmd
Recompile SI files with slight adjustment based on arXiv edits

Cascade food webs are more likely to be stable than small-world or scale-free networks at equivalent magnitudes of complexity (note that $C = 1$ for all above rows). A higher number of stable $\mathbf{M}$ than $\mathbf{A}$ was found given $S \geq 27$.

@@

\clearpage

>>>>

Cascade food webs are more likely to be stable than small-world or scale-free networks at equivalent magnitudes of complexity (note $C = 1$ for all above rows). A higher number of stable $\mathbf{M}$ than $\mathbf{A}$ was found given $S \geq 27$.

@@
